Project Proposal

### 2024-11-17 CURJ_IDS702Projectproposal.qmd

```{r}
merged_df <- merge(all_states_final, prop_tax, by = "FIPS", 
              all.x = TRUE, all.y = TRUE)

#merged_df[sample(nrow(all_states_final), 10), ]
#colSums(is.na(final_df))

>>>>

merged_df <- merge(all_states_final, prop_tax, by = "FIPS", 
              all.x = TRUE, all.y = TRUE)

#merged_df[sample(nrow(all_states_final), 10), ]
#colSums(is.na(final_df))
```
